\section{Ten-fold Way}

We begin our discussion with a background for this classification.  The
classification of topological phases with different non-unitary symmetries in
non-interacting picture, are in essence, the classification of $N\times N$
matrices by its response to three discrete symmetries: time reversal symmetry
($T$), charge conjugation/particle hole symmetry ($C$), and chiral/sub-lattice
symmetry ($S$). As for those unitary symmetries, one can in principle, block
diagonalize the Hamiltonian
$H=\mathrm{diag}(H^{\lambda_1},H^{\lambda_2},\cdots)$, such that each block
$H^{\lambda_i}$ is labeled by irreducible representations $\lambda_i$, and it
has no memory of the unitary symmetries. Then, our classification is
applied to those blocks and still holds.

It will be found that, those $T,C$ are the only two meaningful non-unitary
symmetries of the Single-particle system, and there are in total 10 different
ways in which the Single-particle Hamiltonian could respect the three symmetries
$T,C$, and $S=TC$. Now we explain in detail, about the reason why we care about, and only
care about these three symmetries $T,C,$ and $S$.

\subsection{The symmetries of Single-particle Hamiltonian}
\label{sec:The symmetries of Single-particle Hamiltonian}

According to Wigner's theorem, symmetries of physical system can either be
unitary represented, or anti-unitarily represented. Here we show that in the
case of anti-unitary symmetries, there are only 2 different kinds of them that a
Single-particle Hamiltonian in first-quantized space can have. Actually, there
can be more anti-unitary symmetries than this. But under reasonable assumptions,
we can limit our discussion in only this two types.

The Single-particle Hamiltonian acting on Fock space is
\begin{equation}
\label{eq:H-2nd}
\hat{H} = \sum_{A,B} \hat\psi^\dagger_A H_{AB} \hat\psi_{B}
\end{equation}
where $H_{AB}$ are just complex numbers, $\hat\psi^\dagger_A$ and $\hat\psi_B$
are creation and annihilation operators acting on Fock space.

Here and henceforth, we will add a hat $\hat{}$ to all operators in Fock space
to stress that it acts on Second-quantized Fock space.  A symmetry of the
Hamiltonian, represented as an operator $\hat{U}$, must have:
\begin{equation}
\label{eq:sym-in-2nd-1}
\hat{U}\hat{H}\hat{U}^{-1} = \hat{H}
\end{equation}

We expect $\hat{U}$ to change the creation/annihilation operators in two different
ways. First, it may only permute the creation/annihilation operators:
\begin{subequations}
	\label{eq:sym-in-2nd-permute}
	\begin{align}
	\label{eq:sym-in-2nd-permute-1}
	\hat{\psi}'_A = 
	\hat{U} \hat\psi_A \hat{U}^{-1} &=
	\sum_B (u^\dagger)_{AB} \hat\psi_B \\
	\label{eq:sym-in-2nd-permute-2}
	\hat\psi'^\dagger_A =
	\hat{U} \hat\psi^\dagger_A \hat{U}^{-1} &= 
	\sum_B  \hat\psi^\dagger_B u_{AB}
	\end{align}
\end{subequations}
Where $u$ is some matrix implementing the permutation.
Or, it may interchange the role of creation/annihilation operators:
\begin{subequations}
	\label{eq:sym-cc}
	\begin{align}
	\label{eq:sym-cc-1}
	\hat{\psi}'_A = 
	\hat{U} \hat\psi_A \hat{U}^{-1} &=
	\sum_B (u^*)^\dagger_{AB} \hat\psi^\dagger_B \\
	\label{eq:sym-cc-2}
	\hat\psi'^\dagger_A =
	\hat{U} \hat\psi^\dagger_A \hat{U}^{-1} &= 
	\sum_B  \hat\psi_B u^*_{BA}
	\end{align}
\end{subequations}
Where $u^*$ is some other matrix implementing the interchange. We write complex
conjugation $u^*$ instead of $u$ for convenience. In both cases (permute or
interchange), to conserve the anticommutation relation between
$\hat\psi^\dagger_A$ and $\hat\psi_B$ operators, one can easily show that $u$
should be a unitary matrix.

Also, $\hat{U}$ may be linear or anti-linear. The different combinations of these
conditions give us 1 unitary symmetry, 2 anti-unitary symmetries, and 1 special
symmetry, to be explained below.

\paragraph{Case 1: Unitary Symmetry}

Assume the symmetry just permutes the creation/annihilation operators, as in
equation~\ref{eq:sym-in-2nd-permute}, and assume it is linear in
Second-quantized Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=i$. The permutation
relation~\ref{eq:sym-in-2nd-permute} plugged into
equation~\ref{eq:sym-in-2nd-1}, gives
\begin{equation}
u H u^{-1} = H
\end{equation}
Therefore, in this case the symmetry is unitarily realized in First-quantized
Hamiltonian $H_{AB}$.

\paragraph{Case 2: Anti-unitary T Symmetry}
Assume the symmetry just permutes the creation/annihilation operators, as in
equation~\ref{eq:sym-in-2nd-permute}, but assume it is anti-linear in
Second-quantized Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=-i$. The permutation
relation~\ref{eq:sym-in-2nd-permute} plugged into
equation~\ref{eq:sym-in-2nd-1}, gives a different result, since
$\hat{U}H_{AB}\hat{U}^{-1} = H_{AB}^*$ now.
\begin{equation}
u H^* u^\dagger = H
\end{equation}
Or:
\begin{equation}
uK H u^t K = uK H (uK)^{-1} = H
\end{equation}
where $K$ is complex conjugation. This symmetry is called Time-reversal
symmetry, and is realized in First-quantized Hamiltonian as an anti-unitary
operator $T= uK$.

\paragraph{Case 3: Anti-unitary C Symmetry}
Assume the symmetry just interchange the creation/annihilation operators, as in
equation~\ref{eq:sym-cc}, but assume it is linear in Second-quantized
Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=i$. The interchange
relation~\ref{eq:sym-cc} plugged into equation~\ref{eq:sym-in-2nd-1}, gives:
\footnote{
	Note that in calculating this, $\sum_i\hat\psi^\dagger_i \hat\psi_i =
	\id$ on 1st-quantized single-particle Hilbert space.
}
\begin{equation}
\label{eq:sym-C-cond}
u (H-\frac{1}{2}\tr(H))^t u^\dagger = - (H-\frac{1}{2}\tr(H))
\end{equation}

Taking the trace of above equality will give $2\tr(H)=N\tr(H)$, since
in solids $N>>2$, we must have $\tr(H)=0$. Then the above equality
simplifies into \footnote{note that $H^t = H^*$ for Hermitian $H$}:
\begin{equation}
u H^* u^\dagger = uK H (uK)^{-1} = -H
\end{equation}
This type of symmetry is called charge-conjugation symmetry. It is
also called particle-hole symmetry in condensed matter physics. It is realized
as $C=uK$ with $C H C^{-1} = -H$ for 1st-quantized single-particle Hamiltonian.

\paragraph{Case 4: Unitary S Symmetry}
Assume the symmetry now interchange the creation/annihilation operators, as in
equation~\ref{eq:sym-cc}, and assume it is anti-linear in Second-quantized
Hamiltonian, i.e. $\hat{U}i\hat{U}^{-1}=-i$. The interchange
relation~\ref{eq:sym-cc} plugged into equation~\ref{eq:sym-in-2nd-1}, gives:
\begin{equation}
\label{eq:sym-S-cond}
u (H-\frac{1}{2}\tr(H)) u^\dagger = - (H-\frac{1}{2}\tr(H))
\end{equation}
and since $N>>2$, we have $\tr(H)=0$. Then
\begin{equation}
u H u^\dagger = -H
\end{equation}
This symmetry will be called the chiral symmetry, denoted $\hat{S}=u$. It is
unitarily realized in First-quantized Hamiltonian, but since $\{S,H\}=0$ instead
of $[S,H]=0$, it is not a traditional symmetry that we are used to. Also, it is
easy to see that $S$ is a combination of $T$ and $C$,\footnote{In fact, we could have
	defined $S=TC$ or $S=CT$, and obtained the same result.} and the symmetry
property of Hamiltonian under $T$ or $C$ uniquely defined the symmetry property
of Hamiltonian under $S$. But there is one exception. When the
Hamiltonian does not obey $T$ and $C$, it may or may not obey $S=TC$ as a
whole.

\paragraph{Squaring of $T,C,S$} 
Squaring of $T/C$ symmetry operators should be proportional to identity $\id$,
hence it is only a phase as they are unitary.
This can be viewed from two perspectives. First, we expect the system, after
applying twice of symmetry operation $T/C$, should come back to the same state, except
a possible phase difference. Second, $T^2/C^2$ commutes with all
$T/C$ symmetric Hamiltonians (easy to derive) in all irreducible representations
of unitary symmetries (to be explained later), therefore by Schur's lemma, they
must be proportional to a constant, which is a phase.

It is easy to find that this phase $e^{i\delta}$should be $\pm1$. For example, let $T=uK$,
then $T^2=uu^*$, and $(uu^*)u = u(u^*u)$ gives us $e^{2i\delta}=1$, hence
$e^{i\delta}=\pm1$.

But the square of $S$ is tricky. Since $S=TC=u_T u_C^*$, and each unitary matrix
$u_T$ and $u_C$ has a phase freedom (as they acts on creation/annihilation
operators), we can always pick a phase such that $S^2$ is some phase we want.
Sometimes we pick $S^2=1$. Sometime we want $\{T,C\}=0$, and pick another specific
phase for $S^2$.\footnote{This is a bit troublesome. First we denote
	$T^2=\varepsilon_T$, $C^2=\varepsilon_C$, then it can be found that
	$(u_T)^t=\varepsilon_T u_T$, $(u_C)^t = \varepsilon_C u_C$. Then, with
	$S=u_Tu_C^*$, we have $S^\dagger=\varepsilon_C\varepsilon_Tu_Cu_T^* =
	\varepsilon_C\varepsilon_T CT$, or $CT= \varepsilon_C\varepsilon_TS^\dagger$.
	Since $TC+CT=0$, we have $S+\varepsilon_C\varepsilon_T S^\dagger=0$, or
	$S^2=-\varepsilon_C\varepsilon_T$.}

\paragraph{Why Ten Classes} For the three unitary symmetries under
consideration, as will be mentioned, $S$ symmetry is a combination of $T$ and
$C$, $S=TC$. It will be obtained that $T^2=\pm 1$, $C^2=\pm 1$, and $S^2$ is
undetermined (depending on the phase choice\footnote{To be explained later.} we
give for $T$ and $C$). Therefore, there are in total 10 different possible ways
that this 3 symmetries could be combined together: We denote $T^2=0$ ($C^2=0$)
to symbolize that the system does not follow $T$($C$) symmetry. Then
$T^2=0,\pm1$ and $C^2=0,\pm1$ gives us $3\times 3=9$ different ways. But if
$T^2=C^2=0$, $S$ may or may not conserve. Therefore, we have $9-1+2=10$
different possible ways. In each way the topological invariants of the
Hamiltonian respecting these symmetries are tabulated in Figure.1
in\cite{Ludwig2016}. Each class is given a name ($\mathrm{A}$, $\mathrm{AII}$,
etc.), and their properties in different spatial dimensions respect a periodic
structure. For the class $A$ and class $AII$, they are named complex classes and
respect a $2$-fold period. For the other eight classes are named real classes
and respect a $8$-fold period, which is why we only listed the first $0\to 7$
spatial dimensions in Table~\ref{tab:master-table2}.

\subsection{Dealing with Unitary Symmetries}
\label{sec:Dealing with Unitary Symmetries}

As mentioned, we could module out those unitary symmetries. This statement is
made precise by the following theorem about unitary symmetries of the Hamiltonian.
\begin{thm}[Diagonalization of Hamiltonian in unitary representation]
	This space $\mathcal{V}$ decomposes into a direct sum of vector spaces
	$\mathcal{V}_\lambda$ associated with the irrep (irreducible
	representations, labeled by $\lambda$) of $G_0$.
	\begin{equation}
	\mathcal{V} = \oplus_\lambda m_\lambda \mathcal{V}_\lambda
	\end{equation}
	where $m_\lambda$ denotes the multiplicity of $\lambda$th irrep.
	Denote the dimension of each irrep as $d_\lambda$.
	
	In each vector space $\mathcal{V}_\lambda$, one can choose a
	(orthogonal) basis of the form:
	\begin{equation}
	\ket{v^{(\lambda)}_\alpha} \otimes \ket{w^{(\lambda)}_k}
	\end{equation}
	where
	\begin{itemize}
		\item $G_0$ acts only only $\ket{w^{(\lambda)}}_k$,
		$k=1,\cdots,d_\lambda$,
		\item $H$ acts only on $\ket{v^{(\lambda)}}_\alpha$,
		$\alpha=1,\cdots,m_\lambda$.
	\end{itemize}
\end{thm}
Therefore, with all unitary symmetries ignored, we are classifying how
Hamiltonian will be like when it respects, in 10 different ways, the
combinations of $T,C,S$ symmetries.

\paragraph{Differently Realized Anti-unitary Symmetries}
It should be noted that there is still a freedom of unitary matrix that
implements the $T$ or $C$ symmetry. Therefore, we could have, for example, two
different time-reversal symmetries $T_1 = u_1K$ and $T_2= u_2 K$. They are
obviously related by a unitary matrix, say $T_1 = u_{12} T_2$. And we could
easily get that $u_{12}$ is also a unitary symmetry of the Hamiltonian (if the
Hamiltonian respect both $T_1$ and $T_2$). Therefore, upon enlarging the
symmetry group $G_0$ to include the element $u_{12}$ and repeat the process
described in the theorem above, we only have one time-reversal symmetry. Similar
analysis could be done for the $C$ symmetry as well.

\paragraph{The Tenfold Way}

The Tenfold Way, is originally the ten different ways to write down a
Hamiltonian when there are ten different combinations of symmetries that the 
system respect. The classes of Hamiltonian (or more precisely, the evolution
operators $e^{itH}$) are tabulated in Figure.1 of \cite{Ludwig2016}. Ludwig
classified the topological insulators in each spatial dimension by computing the
homotopy groups for each dimension. On the other hand, this classification can
also be done using $K$-theory.

\paragraph{Translational Symmetry}

Since we are classifying in the solids, it is natural to expect translational
symmetry to present. Also, the addition of translational symmetry not only
																		
					  

																				
produces the same classification\footnote{This is still a mystery to me which this is true. The
	exact reason is related to some isomorphism between certain homotopy groups.
	Interested reader could see Ludwig's lecture
	\href{http://boulderschool.yale.edu/2016/boulder-school-2016-lecture-notes}{here}
	for a clue.}, but also generalize to arbitrary dimensions.

The Hamiltonian in $k$-space that preserve these three discrete symmetries
should follow\footnote{It is easy to anticipate the change $k\to -k$ for
	anti-unitary symmetries, since they change the phase factor when one Fourier
	transform the Hamiltonian.}:
\begin{subequations}
	\begin{align}
	\label{eq:T-sym-Hk}
	TH(k)T^{-1} &= H(-k) \\
	\label{eq:C-sym-Hk}
	CH(k)C^{-1} &= -H(-k) \\
	\label{eq:S-sym-Hk}
	SH(k)S^{-1} &= -S(k)
	\end{align}
\end{subequations}

